A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-18 results.tex
fixed spacing
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@645 ccdd05d5-56c1-461a-bf98-85f6876523b4

For each run, we performed about $10^4$ injections into our mock dataset.  Injections were 2PN post-Newtonian inspiral waveforms with component masses independently and identically distributed in $[1, 3]$ $M_\odot$.  Injections were tapered \editorial{Check --taper-injection option with Drew.} at a frequency of 10~Hz where they enter the Advanced \textsc{ligo} detection band.  This dictated that the longest injection waveform had a duration of {\color{red} 1~777~s}.  In order to guarantee that no two injection waveforms overlapped in the data, the coalescence times of injections were spaced apart by {\color{red} 2~000~$\pm 100$~s}.  For the sake of economizing disk space, we simultaneously analyzed {\color{red} 16 statistically independent sets} of about $10^3$ injections apiece in the same {\color{red} 14 day} stretch of mock strain data.

>>>>

For each run, we performed about $10^4$ injections into our mock dataset.  Injections were 2PN post-Newtonian inspiral waveforms with component masses independently and identically distributed in $[1, 3]$ $M_\odot$.  Injections were tapered \editorial{Check --taper-injection option with Drew.} at a frequency of 10~Hz where they enter the Advanced \textsc{ligo} detection band.  This dictated that the longest injection waveform had a duration of {\color{red} 1~777~s}.  In order to guarantee that no two injection waveforms overlapped in the data, the coalescence times of injections were spaced apart by {\color{red} 2~000~$\pm$~100~s}.  For the sake of economizing disk space, we simultaneously analyzed {\color{red} 16 statistically independent sets} of about $10^3$ injections apiece in the same {\color{red} 14 day} stretch of mock strain data.
